Stage-Splitting a Modal Language

### 2014-06-13 paper/semantics.tex
added more careful reification
changed 'table' to 'context' in a few spots

Abstractly, we can think of our evaluation as proceeding in the standard way for stage-1 code. When the evaluator encounters a $\next \{e\}$ expression, it places $e$ off to the side in a table and replaces the whole expression with a reference to the table entry.  These references are then passed around as stage-1 values for $\fut$ types.  But what if $e$ contains $\prev$ expressions?  To ensure that all stage-1 code is evaluated before any stage-2 code, we must evaluate all of the 1-code contained in $e$ before inserting it into the table.  This entails searching $e$ for all contained $\prev$s and evaluating them in place.

More formally, evaluation comprises the folowing judgments:

@@

The evaluation judgment is very similar to standard call-by-value evaluation, as goal 1 would suggest.  The input to evaluation is a stage-1 expression (usually $e$), as well as two administrative contexts ($\Gamma$ and $\Xi$), covered later.  Evaluation has two outputs: the {\em future table} (usually $\xi$) and the {\em partial value} (usually $v$).  We cover the latter first.  The partial value is essentially the result of the first-stage portion of $e$, and must be a 1-value of the same type as $e$.  As usual, this means that $v$ must be composed only of base primitives, tuples, injections, and lambdas (corresponding to base types, products, sums, and functions).  Analogously, the value corresponding to $\fut$ is a construct called a {\em hatted variable} (written $\hat y$), which signifies a reference to some stage-2 computation.

@@

\begin{enumerate}
\item For some $\colone{e}{A}$ containing no $\next$ expressions, the semantics is derivationally equivalent to standard call-by-value evaluation.
\item Second-stage cost is identical to the erasure semantics.
\item First stage cost is different that erasure, do to speculation.  We always evaluate stage-1 code once, which increases cost, except when that stage-1 code was inside a 2-lambda that got evaluated many times.
\end{enumerate}

>>>>

Abstractly, we can think of our evaluation as proceeding in the standard way for stage-1 code. When the evaluator encounters a $\next \{e\}$ expression, it places $e$ off to the side in a context and replaces the whole expression with a reference to the context entry.  These references are then passed around as stage-1 values for $\fut$ types.  But what if $e$ contains $\prev$ expressions?  To ensure that all stage-1 code is evaluated before any stage-2 code, we must evaluate all of the 1-code contained in $e$ before inserting it into the table.  This entails searching $e$ for all contained $\prev$s and evaluating them in place.

More formally, evaluation comprises the following judgments:

@@

The evaluation judgment is very similar to standard call-by-value evaluation, as goal 1 would suggest.  The input to evaluation is a stage-1 expression (usually $e$), as well as two administrative contexts ($\Gamma$ and $\Xi$), covered later.  Evaluation has two outputs: the {\em future context} (usually $\xi$) and the {\em partial value} (usually $v$).  We cover the latter first.  The partial value is essentially the result of the first-stage portion of $e$, and must be a \bbone-value of the same type as $e$.  As usual, this means that $v$ must be composed only of base primitives, tuples, injections, and lambdas (corresponding to base types, products, sums, and functions).  Analogously, the value corresponding to $\fut$ is a construct called a {\em hatted variable} (written $\hat y$), which signifies a reference to some stage-2 computation.  The mapping between these hatted variables and stage-two expressions is

@@

\begin{enumerate}
\item For some $\colone{e}{A}$ containing no $\next$ expressions, the semantics is derivationally equivalent to standard call-by-value evaluation.
\end{enumerate}
